[dcpo_demsupport]

### 2020-07-04 paper/dcpo_demsupport.Rmd
clean up

```{r dcpo_input}
dcpo_input_raw1 <- read_csv("data/dcpo_input_raw.csv", col_types = "cdcddcd") %>% 
  filter(!(str_detect(item, "army_wvs") & # WVS obs identified as problematic by Claassen 
    ((country=="Albania" & year==1998) |
         (country=="Indonesia" & (year==2001 | year==2006)) |
         (country=="Iran" & year==2000) |
         (country=="Pakistan" & (year==1997 | year==2001)) | # 1996 in Claassen
         (country=="Vietnam" & year==2001)) |
    (str_detect(item, "strong_wvs") &
         ((country=="Egypt" & year==2012) |
              (country=="Iran" & (year==2000 | year==2007)) | # 2005 in Claassen
              (country=="India") |
              (country=="Pakistan" & (year==1997 | year==2001)) | # 1996 in Claassen
              (country=="Kyrgyzstan" & (year==2003 | year==2011)) |
              (country=="Romania" & (year==1998 | year==2005 | year==2012)) |
              (country=="Vietnam" & year==2001))) |
      (country %in% c("Puerto Rico", "Northern Ireland", 
                      "SrpSka Republic", "Hong Kong SAR China")))) %>%
  with_min_yrs(2)

@@

>>>>

```{r dcpo_input}
dcpo_input_raw1 <- read_csv("data/dcpo_input_raw.csv", col_types = "cdcddcd") %>% 
  filter(!(str_detect(survey, "army_wvs") & # WVS obs identified as problematic by Claassen 
                 ((country=="Albania" & year==1998) |
                      (country=="Indonesia" & (year==2001 | year==2006)) |
                      (country=="Iran" & year==2000) |
                      (country=="Pakistan" & (year==1997 | year==2001)) | # 1996 in Claassen
                      (country=="Vietnam" & year==2001)) |
                 (str_detect(item, "strong_wvs") &
                      ((country=="Egypt" & year==2012) |
                           (country=="Iran" & (year==2000 | year==2007)) | # 2005 in Claassen
                           (country=="India") |
                           (country=="Pakistan" & (year==1997 | year==2001)) | # 1996 in Claassen
                           (country=="Kyrgyzstan" & (year==2003 | year==2011)) |
                           (country=="Romania" & (year==1998 | year==2005 | year==2012)) |
                           (country=="Vietnam" & year==2001))) |
                 (country %in% c("Puerto Rico", "Northern Ireland", 
                                 "SrpSka Republic", "Hong Kong SAR China")))) %>%
  with_min_yrs(2)

@@

```{r country_years}
dcpo_input_cy <- dcpo_input_raw1 %>% 
  dplyr::select(country, year) %>% 
  unique()

save(dcpo_input_cy, file = here::here("data", "dcpo_input_cy.rda"))
```
